Crop diversification in a game against nature in a mediterranean agro-ecosystem

### 2020-01-24 risk-percption.Rmd
fresh priors for newborns

```{r}
reproduce <- function(individuals, food_ratio = 0.7) {
  individuals %>%
    left_join(life_table, by = 'age') %>% 
    mutate(fertility_reduction = pgamma(food_ratio, shape = fertility_shape, scale = fertility_scale),
           reproduced = rbernoulli(n(), fertility_rate / 2 * fertility_reduction)) %>% # divide by two to make everyone female
    filter(reproduced == TRUE) %>% # if nrows == 0, will give a (for some reason unsuppressible) warning
    tally %>% # count births per household
    uncount(n) %>% # repeat rows based on birth count per household
    mutate(age = 0) %>%
    bind_rows(individuals, .) %>%
    ungroup # check for filled na's here?
}

@@

```{r}
reduce(1:600, ~reproduce(.x) %>% die , .init = agents2 %>% mutate(age = sample.int(80, size = 150, replace = TRUE))) %>%
  pull(age) %>% hist
```

>>>>

```{r}
reproduce <- function(individuals, food_ratio = 0.7) {
  individuals %>%
    left_join(life_table, by = 'age') %>% 
    mutate(fertility_reduction = pgamma(food_ratio, shape = fertility_shape, scale = fertility_scale),
           reproduced = rbernoulli(n(), fertility_rate / 2 * fertility_reduction)) %>% # divide by two to make everyone female
    filter(reproduced == TRUE) %>% # if nrows == 0, will give a (for some reason unsuppressible) warning
    tally %>% # count births per household
    uncount(n) %>% # repeat rows based on birth count per household
    mutate(age = 0, alpha = 1.5, beta = 1.5, risk = alpha / (alpha + beta)) %>%
    bind_rows(individuals, .) %>%
    ungroup # check for filled na's here?
}

@@

Ok so next we need to have the birth and death stuff run with all the prior information in it. dont need to propogate the prior exactly, just need to add in a new weak prior. at least propogate the risk number, but not the prior?
```{r}
reduce(1:600, ~reproduce(.x) %>% die , .init = agents2 %>% mutate(age = sample.int(80, size = 150, replace = TRUE))) %>%
  pull(age) %>% hist
```
